Seasonality in governing submesoscale dynamics in the Kuroshio Extension

### 2016-07-06 writeup/rocha_etal.tex
Fixes small ambiguity.

\section{Statistics of the surface lateral velocity tensor}
To study the seasonality in the surface velocity, we calculate the lateral velocity tensor
\begin{equation}
\nabla_h \bf{u}_h = \left[\begin{matrix} u_x & u_y\\ v_x&v_y \end{matrix}\right] \,.
\end{equation}
The components of the lateral velocity tensor are calculated using a centered
second-order finite difference scheme. We then diagnose
the vertical vorticity $\zeta \equiv v_x - u_y$, lateral rate of strain
$\alpha \equiv [(u_x-v_y)^2 + (u_y + v_x)^2]^{1/2}$, and horizontal divergence $\delta \equiv u_x + v_y$.
These diagnostics highlight the submesoscale structures in the flow
\citep[e.g.,][]{capet_etal2008a,shcherbina_etal2013}.

>>>>

\section{Statistics of the surface lateral velocity tensor}
To study the seasonality in the surface velocity, we calculate the lateral velocity gradient tensor
\begin{equation}
\nabla_h \bf{u}_h = \left[\begin{matrix} u_x & u_y\\ v_x&v_y \end{matrix}\right] \,.
\end{equation}
The components of the lateral velocity gradient tensor are calculated using a centered
second-order finite difference scheme. We then diagnose
the vertical vorticity $\zeta \equiv v_x - u_y$, lateral rate of strain
$\alpha \equiv [(u_x-v_y)^2 + (u_y + v_x)^2]^{1/2}$, and horizontal divergence $\delta \equiv u_x + v_y$.
These diagnostics highlight the submesoscale structures in the flow
\citep[e.g.,][]{capet_etal2008a,shcherbina_etal2013}.
